% LaTeX
\begin{thebibliography}{1}

\bibitem{rawDiag}
Christian Trachsel, Christian Panse, Tobias Kockmann, Witold~E. Wolski, Jonas
  Grossmann, and Ralph Schlapbach.
\newblock rawdiag: An r package supporting rational lc–ms method optimization
  for bottom-up proteomics.
\newblock {\em Journal of Proteome Research}, 17(8):2908–2914, July 2018.
\newblock package url: \hvqrurl[qrlink=nolink]{https://bioconductor.org/packages/rawDiag/}, \href
  {https://doi.org/10.1021/acs.jproteome.8b00173}
  {\path{doi:10.1021/acs.jproteome.8b00173}}.

\bibitem{rawrr}
Tobias Kockmann and Christian Panse.
\newblock The rawrr {R} package: Direct access to {Orbitrap} data and beyond.
\newblock {\em Journal of Proteome Research}, 20(4):2028–2034, March 2021.
\newblock package url: \hvqrurl[qrlink=nolink]{https://bioconductor.org/packages/rawrr/},
  \href{https://doi.org/10.1021/acs.jproteome.0c00866}
  {\path{doi:10.1021/acs.jproteome.0c00866}}.

\bibitem{MsBackendRawFileReader}
{Christian Panse, Tobias Kockmann}.
\newblock {MsBackendRawFileReader}, 2021.
\newblock package url: \hvqrurl{https://bioconductor.org/packages/MsBackendRawFileReader},
  \href {https://doi.org/10.18129/B9.BIOC.MSBACKENDRAWFILEREADER}
  {\path{doi:10.18129/B9.BIOC.MSBACKENDRAWFILEREADER}}.

\bibitem{MetaboAnnotation}
Johannes Rainer, Andrea Vicini, Liesa Salzer, Jan Stanstrup, Josep~M. Badia,
  Steffen Neumann, Michael~A. Stravs, Vinicius Verri~Hernandes, Laurent Gatto,
  Sebastian Gibb, and Michael Witting.
\newblock A modular and expandable ecosystem for metabolomics data annotation
  in R.
\newblock {\em Metabolites}, 12(2):173, February 2022.
\newblock package url: \hvqrurl{https://bioconductor.org/packages/MetaboAnnotation/}, \href
  {https://doi.org/10.3390/metabo12020173} {\path{doi:10.3390/metabo12020173}}.
\end{thebibliography}
